Development Of Parallel Matrix Operations

### 2011-02-15 paper/paper.tex
Add spec's of the machine the timing numbers were recorded on.
Add small section to conclusion

@@

>>>>

All timing numbers were taken by running jobs on the RIT CS department's
paradise SMP machine. The machines stat's at the time of writing: 
Four Sun UltraSPARC-IV dual-core CPUs, eight processors, 1.35 GHz clock, 16 GB
main memory.
\subsection{Matrix-Vector Multiplication}

@@

We were able to glean interesting results from the data points we retreived.
However the size of the matrices we could create was limited by JVM's maximum heap size.
It may be worth wile to explore running the implementented
algorithms on different architectures with possibly larger JVM heap upper
bounds. Since in general we saw increased peformance by increasing the size of
N, the point at which this is no longer true for our implementations would be a
helpful thing to know.
